Comparing R packages for calculation of persistent homology

### 2020-02-20 tdabench-paper/tdabench.Rmd
updated panel labels

Tori do not trivially generalize to other dimensions, but circles do.
Benchmarking on a circular point cloud permits confirmation of the pattern in Figure \ref{fig:tor} while also revealing how the libraries compare as dataset dimension increases.
Figure \ref{fig:cir} exhibits the resulting data for a 2-dimensional circle (panel A), 3-dimensional sphere (panel B), and 4-dimensional hypersphere (panel C).
When the dataset dimension equals 2, GUDHI practically matches Ripser's performance in outpacing Dionysus.
However, in the case of the 3-dimensional sphere, the pattern visualized in Figure \ref{fig:tor} for the 3-dimensional torus is again present.
By the 4th dimension, the gap between Ripser and GUDHI widens.
Of note, missing points for larger datasets in Figure \ref{fig:cir} are not plotted if and only if calculating persistent homology caused an error due to insufficient RAM.
Thus, for the hypersphere, Ripser was able to calculate persistent homology for a dataset with approximately 3 times as many points as Dionysus and over 2 times as many as GUDHI.
Interestingly, all curves plotted in Figure \ref{fig:cir} grow polynomially with respect to the number of points (see Supplement for regression details).

\begin{widefigure}
  \centering
  \includegraphics[height=2in]{../Figures/Final_Figures/fig2.png}
  \caption{
    \textbf{Calculating persistent homology of round point clouds of varying dimensions with three TDA libraries.}
    Average runtime (mean $\pm$ SD, $n=10$) for each TDA library (denoted by color) is plotted against point cloud size and faceted by data dimension.
    Panel 1 compares library performance for a 2-dimensional circular point cloud; panel 2 for a 3-dimensional spherical point cloud; and panel 3 for a 4-dimensional hyperspherical point cloud.
    Maximum feature dimensions (one less than data dimension) were calculated in each case.
  }
\label{fig:cir}
\end{widefigure}

>>>>

Tori do not trivially generalize to other dimensions, but circles do.
Benchmarking on a circular point cloud permits confirmation of the pattern in Figure \ref{fig:tor} while also revealing how the libraries compare as dataset dimension increases.
Figure \ref{fig:cir} exhibits the resulting data for a 2-dimensional circle (left panel), 3-dimensional sphere (center panel), and 4-dimensional hypersphere (right panel).
When the dataset dimension equals 2, GUDHI practically matches Ripser's performance in outpacing Dionysus.
However, in the case of the 3-dimensional sphere, the pattern visualized in Figure \ref{fig:tor} for the 3-dimensional torus is again present.
By the 4th dimension, the gap between Ripser and GUDHI widens.
Of note, missing points for larger datasets in Figure \ref{fig:cir} are not plotted if and only if calculating persistent homology caused an error due to insufficient RAM.
Thus, for the hypersphere, Ripser was able to calculate persistent homology for a dataset with approximately 3 times as many points as Dionysus and over 2 times as many as GUDHI.
Interestingly, all curves plotted in Figure \ref{fig:cir} grow polynomially with respect to the number of points (see Supplement for regression details).

\begin{widefigure}
  \centering
  \includegraphics[height=2in]{../Figures/Final_Figures/fig2.png}
  \caption{
    \textbf{Calculating persistent homology of round point clouds of varying dimensions with three TDA libraries.}
    Average runtime (mean $\pm$ SD, $n=10$) for each TDA library (denoted by color) is plotted against point cloud size and faceted by data dimension.
    Left panel compares library performance for a 2-dimensional circular point cloud; center panel for a 3-dimensional spherical point cloud; and right panel for a 4-dimensional hyperspherical point cloud.
    Maximum feature dimensions (one less than data dimension) were calculated in each case.
  }
\label{fig:cir}
\end{widefigure}
